---
title: "Good and Bad Plot"
author: "Chloe"
date: "2023-03-30"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo= TRUE, 
                      warning = FALSE, 
                      message = FALSE)
```


## Introduction 

Today I will make a good and bad plot, by using a data set from the 1974 *Motor Trend* magazine publication on motor trend car road tests. 32 cars were studied, and I used 3 categories of automobile design.

### Load Data
```{r}
library(tidyverse)
library(here)
library(dplyr)
library(ggrepel) #repels data for easier viewing
library(reshape2) #used for circular data graph in the bad plot
```

### Inspect Data 
```{r}
View(mtcars) #viewed car data
glimpse(mtcars)
```
 

### Make a Bad Plot 

Shown below is my bad plot with derived data from the cars data set. This plot is considered to be "bad" due to the following reasons: 

* ambiguous & useless legend that shows information for a separate data category
* pie graph (automatic no-no) 
* non-specific axis labels & plot title
* overwhelming colors used within the plot
* cluttered data labels that may also be overshadowed by plot colors
* unclear data points

```{r}
mtcars %>% 
  ggplot(aes(x = mpg, 
             y = hp,
             fill = cyl,
             na.rm=FALSE, 
             label = rownames(mtcars))) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 12),
        panel.grid = element_line(color = "pink"), 
        panel.background = element_rect(fill = "violet"), 
        legend.key = element_rect(color = "beige")) +
  geom_bar(width=0.5, stat="identity", color = "green") + 
  coord_polar("y", start=0) + #combined coord_polar w/ geom_bar to create basic pie graph
  geom_text_repel() + #separated data
  ggtitle("cars mpg and hp") 

#to save the graph
ggsave(here("Good_Plot_Bad_Plot", "output", "badplot1.png"))

```


### Make a Good Plot

Below is my attempt at creating a good plot using the same car data. What makes this a good plot is: 

* non-distracting color scheme
* a more specific plot title and axis labels
* the plot is easier to read than the first plot, although the data points could have been smaller and less crowded 
* more of a useful graph for understanding the data

```{r mtcars}
ggplot(mtcars, aes(x = hp, 
                   y = mpg, 
                   label = rownames(mtcars))) + 
  labs(x = "Horsepower", 
       y = "Miles Per Gallon") + 
  theme_bw() + 
  geom_text_repel() + #repels to make text easy to read
  geom_count(color = 'violet') + 
  ggtitle("Comparison of Horsepower and MPG in Cars from 1974") + 
  theme(plot.title = element_text(hjust = 0.5))

#save good plot 
ggsave(here("Good_Plot_Bad_Plot", "output","goodplot.png"))

```


